Computing properties of independent sets by generic programming tensor networks \thanks{\funding{...}}

### 2021-09-11 paper/paper.tex
small revision on section 2

\begin{example}
$C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is a tensor network representing $C_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$,
where $i,j,k$ in the output tensor are open edges.
Its hypergraph representation is shown below, where we use different colors to annotate different hyperedges and open circles to denote open edges.

>>>>

\begin{example}
$C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is a tensor network representing $C_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$,
where $i,j,k$ in the output tensor are open edges (note that $j$ is not an open edge and thus summed over).
Its hypergraph representation is shown below, where we use different colors to annotate different hyperedges.
